ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-11-30 proposal.tex

@@

\vspace{12pt}
\noindent The manual steering system is modeled by a twentieth order transfer function. After considering the system costs that come with a higher order transfer function and the need to achieve a sufficient best fit percentage, it is clear that a twentieth order transfer function is the best estimation of the system. \autoref{manualSteerCoeffA} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage A signal. \autoref{manualSteerCoeffB} shows the coefficients of the twentieth order transfer function for the output steering angle with respect to the input torque voltage B signal.

\begin{figure}[h]
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
      \bottomrule
    \end{tabular}}
    \begin{center}
    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
      \bottomrule
    \end{tabular}}
    \end{center}
    \label{manualSteerCoeffA}
	\caption{Manual Mode Steering Transfer Function Torque Voltage A Coefficient Table}
\end{figure}
\begin{figure}[h]
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
      \bottomrule
    \end{tabular}}
	\begin{center}
	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
      \midrule
      1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
      \bottomrule
    \end{tabular}}
	\end{center}	
	\label{manualSteerCoeffB}
	\caption{Manual Mode Steering Transfer Function Torque Voltage B Coefficient Table}
\end{figure}

@@

\vspace{12pt}
\noindent The model of the by-wire acceleration system is a fourth order ARX model. The fourth order ARX model defined in \autoref{byWireAccelEq} represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$. 
\begin{figure}[h]
	\begin{equation}
		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
	\end{equation}
	%
	where na = 4, nb = 4, nk = 0, and, 
	%
	\begin{equation}
		A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
	\end{equation}
	\begin{equation}
		B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
	\end{equation}
	\begin{equation}
		B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
	\end{equation}
	\label{byWireAccelEq}
	\caption{By-Wire Mode Acceleration System ARX Model Equations}
\end{figure}

>>>>

  % %
  % \begin{figure}
  %   \centering
  %   \begin{subfigure}[b]{0.48\linewidth}
  %     \centering
  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsTopViewV3}
  %     \caption{}
  %     \label{fig:PowertrainModelCorrectDimsTopViewV3}
  %   \end{subfigure}
  %   \begin{subfigure}[b]{0.48\linewidth}
  %     \centering
  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsFrontViewV4}
  %     \caption{}
  %     \label{fig:PowertrainModelCorrectDimsFrontViewV4}
  %   \end{subfigure}
  %   \begin{subfigure}[b]{0.48\linewidth}
  %     \centering
  %     \includegraphics[width=\textwidth]{figs/fusion360/PowertrainModelCorrectDimsSideViewV4}
  %     \caption{}
  %     \label{fig:PowertrainModelCorrectDimsSideViewV4}
  %   \end{subfigure}
  %   \caption{\subref{fig:PowertrainModelCorrectDimsTopViewV3} Top view,
  %     \subref{fig:PowertrainModelCorrectDimsFrontViewV4} front view, and
  %     \subref{fig:PowertrainModelCorrectDimsSideViewV4} side view of the
  %     proposed disinfecting robot.}
  %   \label{fig:2dViewsDisinfectingRobot}
  % \end{figure}

@@

\vspace{12pt}
\noindent The manual steering system is modeled by a twentieth order transfer
function. After considering the system costs that come with a higher order
transfer function and the need to achieve a sufficient best fit percentage, it
is clear that a twentieth order transfer function is the best estimation of the
system. \autoref{tab:manualSteerCoeffA} shows the coefficients of the twentieth
order transfer function for the output steering angle with respect to the input
torque voltage A signal. %
%
  \begin{table}[hbtp]
    \caption{Manual mode steering transfer function torque voltage A coefficient table. }
    \label{tab:manualSteerCoeffA}
    \centering
	  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
      \begin{tabular}{*{21}{c}}
        \toprule
        $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
        \midrule
        1.224E5 & 4.227E5 & 2.202E6 & 3.54E6 & 7.98E6 & 7.62E5 & 1.071E7 & 6.745E6 & 6.85E6 & 3.006E6 & 2.365E6 & 7.37E5 & 4.669E5 & 1.021E5 & 5.319E4 & 7752 & 3353 & 287.5 & 102.4 & 3.653 & 1\\
        \bottomrule
      \end{tabular}}
    \begin{center}
    	\resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
        \begin{tabular}{*{21}{c}}
          \toprule
          $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
          \midrule
          6.516E4 & -2.944E5 & 2.328E5 & -2.487E5 & 8.25E4 & -3.038E4\\
          \bottomrule
        \end{tabular}}
    \end{center}
  \end{table}
%

\autoref{tab:manualSteerCoeffB} shows the coefficients of
the twentieth order transfer function for the output steering angle with respect
to the input torque voltage B signal. %
%
\begin{table}[hbtp]
	\caption{Manual Mode Steering Transfer Function Torque Voltage B Coefficient Table}
	\label{tab:manualSteerCoeffB}
  \centering
  \resizebox{\linewidth}{!}{% Resize table to fit within \linewidth horizontally
    \begin{tabular}{*{21}{c}}
      \toprule
      $a_0$& $a_1$&$a_2$&$a_3$&$a_4$&$a_5$&$a_6$&$a_7$&$a_8$&$a_9$&$a_{10}$&$a_{11}$&$a_{12}$&$a_{13}$&$a_{14}$&$a_{15}$&$a_{16}$&$a_{17}$&$a_{18}$ &$a_{19}$&$a_{20}$\\
      \midrule
      4.687E4 & 7.037E5 & 2.624E6 & 6.133E6 & 1.197E7 & 1.487E7 & 1.887E7 & 1.446E7 & 1.314E7 & 7.01E6 & 4.79E6 & 1.886E6 & 9.836E5 & 2.937E5 & 1.149E5 & 2.617E4 & 7205 & 1232 & 200 & 23.54 & 1\\
      \bottomrule
    \end{tabular}}
	\begin{center}
    \resizebox{0.4\linewidth}{!}{% Resize table to fit within \linewidth horizontally
      \begin{tabular}{*{21}{c}}
        \toprule
        $b_0$& $b_1$&$b_2$&$b_3$&$b_4$&$b_5$\\
        \midrule
        1.209E4 & 1.855E5 & -2.801E5 & 4.72E5 & -3.976E4 & 7.693E4\\
        \bottomrule
      \end{tabular}}
	\end{center}	
\end{table}
%

@@

\vspace{12pt}
\noindent The model of the by-wire acceleration system is a fourth order ARX model. The fourth order ARX model defined in \autoref{byWireAccelEq} represents the output acceleration pedal position, A(z), based on input torque voltage A, $B_1(z)$, and input torque voltage B, $B_2(z)$. 
% \begin{figure}[h]
	\begin{equation}
		A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t),
	\end{equation}
	%
	where na = 4, nb = 4, nk = 0, and, 
	%
  \begin{align*}
		A(z) &= 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}\\
    B_1(z) &= -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}\\
		B_2(z) &= 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
  \end{align*}
% 	\label{byWireAccelEq}
% 	\caption{By-Wire Mode Acceleration System ARX Model Equations}
% \end{figure}
